Within and beyond: chert procurement patterns during the Upper Palaeolithic in Southwesternmost Iberia

### 2024-07-16 analysis/paper/paper.qmd
- Corrected filter in the shelter graph in stratigraphy.

```{r}
#| label: fig-local-types
#| fig-cap: Variability of local chert types and main petrographic characteristics. a) Type 1 macroscopic appearance (a1) and thin-section (a2). b) Type 3 macroscopic appearance (b1) and thin-section (b2). c-d) Type 2 macroscopic appearance (c1-d1) and thin-section (c2-d2). e-f) Type 4 macroscopic appearance (e-f1) and thin-section (f2-f3). g-h) Type 5 macroscopic appearance (g-h1) and thin section (h2-h3).

@@

```{r}
#| label: fig-distance-types
#| fig-cap: Variability of non-local types and main petrographic characteristics. a-b) Type 6 macroscopic appearance (a1-b1) and thin-section (a2-b2); b1-b2 correspond to a sample covered 100% in white patina. c-d) Type 7 macroscopic appearance (c1-d1) and thin-section (c2-d2) of peloidal facies (c1-c2) and oolitic facies (d1-d2). e-f) Type 8 macroscopic appearance (e-f1) and thin-section (f2-f3); white and black arrows correspond to foraminifera. g) Type 9 macroscopic appearance (g1) and thin-section (g2). Type 10 macroscopic appearance (h1) and thin-section (h2).

@@

# Type per level plots fr Shelter
## Preparing db for the barplots
s_data_plots <- S_dataset %>% # sorting missing values and filtering non-solutrean layers
  filter(RMTYPE != "INDET" & WEIGHT != "0") %>% 
  mutate_at(vars(Layer), ~replace_na(., "ND")) %>% 
  filter(CODE != "B" & Layer != "D" & Layer != "ND") %>% #removing buckets (B)
  mutate(RMTYPE = factor(RMTYPE, levels = c("TYPE 1","TYPE 2", "TYPE 3", "TYPE 4",
                                        "TYPE 5", "TYPE 6","TYPE 7", 
                                        "TYPE 8", "TYPE 9", "TYPE 10", "TYPE 11", "TL")))

>>>>

```{r}
#| label: fig-local-types
#| fig-cap: Variability of local chert types and main petrographic characteristics. a) Type 1 macroscopic appearance (a1) and thin section (a2). b) Type 3 macroscopic appearance (b1) and thin section (b2). c-d) Type 2 macroscopic appearance (c1-d1) and thin section (c2-d2). e-f) Type 4 macroscopic appearance (e-f1) and thin section (f2-f3). g-h) Type 5 macroscopic appearance (g-h1) and thin section (h2-h3).

@@

```{r}
#| label: fig-distance-types
#| fig-cap: Variability of non-local types and main petrographic characteristics. a-b) Type 6 macroscopic appearance (a1-b1) and thin section (a2-b2); b1-b2 correspond to a sample covered 100% in white patina. c-d) Type 7 macroscopic appearance (c1-d1) and thin section (c2-d2) of peloidal facies (c1-c2) and oolitic facies (d1-d2). e-f) Type 8 macroscopic appearance (e-f1) and thin section (f2-f3); white and black arrows correspond to foraminifera. g) Type 9 macroscopic appearance (g1) and thin section (g2). Type 10 macroscopic appearance (h1) and thin section (h2).

@@

# Type per level plots fr Shelter
## Preparing db for the barplots
s_data_plots <- S_dataset %>% # sorting missing values and filtering non-solutrean layers
  filter(RMTYPE != "INDET" & WEIGHT != "0") %>% 
  mutate_at(vars(Layer), ~replace_na(., "ND")) %>% 
  filter(CODE != "B" & Layer != "D" & Layer != "ND" & Layer != "No info") %>% #removing buckets (B)
  mutate(RMTYPE = factor(RMTYPE, levels = c("TYPE 1","TYPE 2", "TYPE 3", "TYPE 4",
                                        "TYPE 5", "TYPE 6","TYPE 7", 
                                        "TYPE 8", "TYPE 9", "TYPE 10", "TYPE 11", "TL")))
